### 2025-01-24 BAI/exercises.tex
Removed code link and added last chapter lecture questions.

>>>>

\begin{exercise}{Continual Learning for Robotic Action}
  \begin{enumerate}
    \item Explain the stability-plasticity dilemma and how it relates to continual learning.
    \item What is Hebbian learning?
    \item Outline the problem of catastrophic forgetting in neural networks and how it can be overcome.
    \item How could continual object recognition be approached?
    \item What are the applications of continual learning in natural language processing?
    \item Compare the state-of-the-art models with biological systems.
    \item How can continual learning be used to model higher-level cognitive functions in artificial systems?
  \end{enumerate}

  \begin{solution}
    \begin{enumerate}
      \item The stability-plasticity dilemma is the trade-off between the ability of a neural network to learn new information (plasticity) and the ability of the network to retain previously learned information (stability). Continual learning is the ability to incrementally learn over time without forgetting.
      \item Hebbian learning is a learning rule that strengthens synaptic connections between neurons that fire together.
      \item Catastrophic forgetting is the phenomenon where a neural network forgets previously learned information when learning new information. This problem can be overcome by using regularization, dynamic architectures, and rehearsal/replay.
      \item Continual object recognition can be approached by using self-organizing networks like Gamma-GWR to learn sequences of objects and by using hybrid models like Growing Dual-Memory (GDM) with memory replay to recognize objects over time.
      \item Applications of continual learning in natural language processing include continual language learning and open challenges in adapting to new tasks and data.
      \item State-of-the-art models are far from providing the flexibility, robustness, and scalability of biological systems. These models are limited in their ability to learn from new data and adapt to changing environments.
      \item Continual learning can be used to model higher-level cognitive functions in artificial systems by providing a framework for learning from new data, adapting to new tasks, and retaining previously learned information.
    \end{enumerate}
  \end{solution}
\end{exercise}
